---
output: 
  html_document:
    self_contained: false
---

```{r include=FALSE, warning=FALSE}
# Note: The following sourcing scripts are separated to allow easier debugging.
# It is ugly, but it's more useful than "Error between Line 8 to 15".
library(lubridate)

# For automatic data pipe

source("./data_import.r")

# For manual imports, remember to comment-out the other.

# source("./data_import_manual.r")
```

```{r include=FALSE, warning=FALSE}
source("./buyer-backlogs.r")
```

```{r include=FALSE, warning=FALSE}
source("./buyer-backlogs-90dayplus.r")
```

```{r include=FALSE, warning=FALSE}
source("./buyer-backlogs-amounts.r")
```

```{r include=FALSE, warning=FALSE}
source("./approver-backlogs.r")
```

```{r include=FALSE, warning=FALSE}
# Switch for whether thetime machine section (historical trends) is used
#   and rendered. Controls read/write to mongodb as well as rendering of
#   the graphs.
# The titles for the timemachine sections will still be included (since
#   they are not R code), thus this is largly a debug option. 
use_time_machine = TRUE
```

```{r include=FALSE, warning=FALSE, eval=use_time_machine}
# NOTE: The following file writes to the specified mongodb, comment out
#         the line while debugging to avoid accidental writes
source("./time_machine-mongo.r")
```

```{r include=FALSE, warning=FALSE, eval=use_time_machine}
source("./time_machine-graphs.r")
```
# Buyer Backlog Report of `r data_date`

```{r echo=FALSE, warning=FALSE, fig.align='center', out.width="100%", out.height="450px"}
# All backlog Reqs, by buyer category, then y-axis by buyer and color by Req Type.
# 'fixedrange' to force the axis to be non-modifiable
backlog_plot_ninv <- backlog_plot %>% 
  filter(Category == "NINV") %>% 
  plot_ly() %>% 
  add_bars(y = ~Buyer,
          x = ~Count,
          color = ~Type,
          type = "bar", 
          colors = c("#00EE00","#EEEE00","#EE0000"),
          width = "16px",
          legendgroup = ~Type) %>% 
  layout(yaxis = list(autorange = "reversed", fixedrange = TRUE), 
         xaxis = list(fixedrange = TRUE), 
         barmode = 'stack')

backlog_plot_se <- backlog_plot %>% 
  filter(Category == "SE") %>% 
  plot_ly() %>% 
  add_bars(y = ~Buyer,
          x = ~Count,
          color = ~Type,
          type = "bar", 
          colors = c("#00EE00","#EEEE00","#EE0000"),
          legendgroup = ~Type, 
          width = "16px",
          showlegend = F) %>% 
  layout(yaxis = list(autorange = "reversed", fixedrange = TRUE), 
         xaxis = list(fixedrange = TRUE), 
         barmode = 'stack')


# On 2019-09-06, a request was made to filter out buyer KL. 
# Consequent code changes had been made to filter this buyer out with a
#   description below the plot.
# On 2019-10-03, a request was made to remove the changes so that the buyer
#   will re-appear in the plot. Thus, previous changes has been removed. 
#   see previous commits (on 'ohio' branch) for code.
backlog_plot_inv <- backlog_plot %>% 
  filter(Category == "INV") %>% 
  plot_ly() %>% 
  add_bars(y = ~Buyer,
          x = ~Count,
          color = ~Type,
          type = "bar", 
          colors = c("#00EE00","#EEEE00","#EE0000"),
          legendgroup = ~Type, 
          width = "16px",
          showlegend = F) %>% 
  layout(yaxis = list(autorange = "reversed", fixedrange = TRUE), 
         xaxis = list(fixedrange = TRUE), 
         barmode = 'stack')

# subplots are ggplot equivalent of facets
subplot(backlog_plot_ninv, backlog_plot_se, backlog_plot_inv, nrows = 3, margin = .03, shareX = TRUE) %>% 
  # No controls around the plot, to be mobile friendly
  config(displayModeBar = FALSE) %>% 
  layout(title = "All Reqs")
```

*Omitted buyer(s) with no backlogs: `r paste(hidden_buyers)`.*


```{r echo=FALSE, out.width="100%", out.height="425px"}
backlog_plot_90dayplus_ninv <- backlog_plot_90dayplus %>% 
  filter(Category == "NINV") %>% 
  plot_ly() %>% 
  add_bars(y = ~Buyer,
          x = ~Count,
          color = ~Type,
          type = "bar", 
          colors = c("#00EE00","#EEEE00","#EE0000"),
          width = "16px",
          legendgroup = ~Type) %>% 
  layout(yaxis = list(autorange = "reversed", fixedrange = TRUE), 
         xaxis = list(fixedrange = TRUE), 
         barmode = 'stack')

backlog_plot_90dayplus_se <- backlog_plot_90dayplus %>% 
  filter(Category == "SE") %>% 
  plot_ly() %>% 
  add_bars(y = ~Buyer,
          x = ~Count,
          color = ~Type,
          type = "bar", 
          colors = c("#00EE00","#EEEE00","#EE0000"),
          width = "16px",
          legendgroup = ~Type,
          showlegend = F) %>% 
  layout(yaxis = list(autorange = "reversed", fixedrange = TRUE), 
         xaxis = list(fixedrange = TRUE), 
         barmode = 'stack')

backlog_plot_90dayplus_inv <- backlog_plot_90dayplus %>% 
  filter(Category == "INV") %>% 
  plot_ly() %>% 
  add_bars(y = ~Buyer,
          x = ~Count,
          color = ~Type,
          type = "bar", 
          colors = c("#00EE00","#EEEE00","#EE0000"),
          width = "16px",
          legendgroup = ~Type,
          showlegend = F) %>% 
  layout(yaxis = list(autorange = "reversed", fixedrange = TRUE), 
         xaxis = list(fixedrange = TRUE), 
         barmode = 'stack') 


subplot(backlog_plot_90dayplus_ninv, backlog_plot_90dayplus_se, backlog_plot_90dayplus_inv, nrows = 3, margin = .03, shareX = TRUE) %>% 
  config(displayModeBar = FALSE) %>% 
  layout(title = "Reqs Over 90 Days")
```

## PP's Approval Worklist

```{r echo=FALSE}
# Approver's backlog overview
# Grouping By Age: 0 to 7, 7 to 14, 14 to 30, 30+
# Grouping By Dollar Amount: <$50k, $50k to $250k, $250k to $500k, $500k+
# Total # of backlog entries
# Since the bins rarely change, the group header is added by hard-coding the # of columns.
kable(approver_kable) %>% 
  kable_styling() %>% 
  add_header_above(c("Grouping By Age (Days)" = 4, "Grouping By Dollar Amount" = 4, " " = 1)) %>% 
  column_spec(9, bold = TRUE) %>% 
  column_spec(c(4), border_right = TRUE, include_thead = TRUE)
```

<P style="page-break-before: always">

### PP's Worklist Details (`r approver_detail_count`)

*Omitted `r (approver_total_count - approver_detail_count)` entries less than $50,000.*

```{r echo=FALSE}
kable(approver_detail_table)%>% 
  kable_styling() %>% 
  add_header_above(c(" " = 1, "Worklist Data" = 3,"Req Details" = 2))
```
<P style="page-break-before: always">

## All Backlog, By Req Age
```{r echo=FALSE}
# This vector holds the buyer counts for this kable, in "NI, SE, INV" order, then add 1 for subtotal line.
# group_rows uses the vector as is for each group.
# row_spec uses cumsum of this value to get the index of last lines of each category
# The index of final Sum row is the sum of the row #s + 1. 
backlog_age_row_num_vec <- as_vector(backlog_age_kable_col_count[[2]]) + 1
kable(backlog_kable) %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 1, "Actionable" = 4, "On Hold" = 1, "Out-to-Bid" = 1, " " = 1)) %>% 
  group_rows(index = c("Non-Inventory" = backlog_age_row_num_vec[1], 
                       "Sourcing Exec." = backlog_age_row_num_vec[2], 
                       "Inventory" = backlog_age_row_num_vec[3],
                       "Total" = 1)) %>% 
  row_spec(cumsum(backlog_age_row_num_vec), italic = TRUE, background = "#EEEEEE") %>% 
  row_spec(sum(backlog_age_row_num_vec) + 1, bold = TRUE)
```
<P style="page-break-before: always">

## Backlog older than 90 days, By Req Amount

```{r echo=FALSE}
# int -> int; add 1 to the given int if it is positive.
# The reason for this function is that, when calculating the # of columns
#   needed for each buyer category (raw values provided by DF 
#   backlog_amt_kable_col_count), 1 needs to be added to each category to
#   include the subtotal row. However, if a category has 0 entries, the code
#   will error out since the number of rows does not add up (i.e. empty 
#   categories does not have a subtotal row in the incoming data).
# This function ensures that 0 will not be incremented when calculating the
#   number of rows needed.
# This is not a perfect solution, since the formatting of subtotal rows 
#   depends on the # of rows data as well. Thus, a unique() is added in the 
#   subtotal formatting row index calculation. 

plus.one.on.positive <- function(n) 
  {if (n > 0) {n+1} else {n}}

backlog_amt_row_num_vec <- as_vector(map(as_vector(backlog_amt_kable_col_count[[2]]), plus.one.on.positive))
kable(backlog_amount_kable) %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 1, "Actionable" = 3, "On Hold" = 1, "Out-to-Bid" = 1, " " = 1)) %>% 
  group_rows(index = c("Non-Inventory" = backlog_amt_row_num_vec[1], 
                       "Sourcing Exec." = backlog_amt_row_num_vec[2], 
                       "Inventory" = backlog_amt_row_num_vec[3], 
                       "Total" = 1)) %>% 
  row_spec(unique(cumsum(backlog_amt_row_num_vec)), italic = TRUE, background = "#EEEEEE") %>% 
  row_spec(sum(backlog_amt_row_num_vec) + 1, bold = TRUE)
```

## PP's Worklist Trend
```{r echo=FALSE, warning=FALSE, out.width="100%", out.height="400px", eval = use_time_machine}
plot_ly(data = approver_worklist_timemachine) %>% 
  add_lines(x = ~Archive_Time, 
            y = ~Cnt, 
            name = "PP's List (> $50K)") %>% 
  # No controls around the plot, to be mobile friendly
  layout(xaxis = list(title = "Date", fixedrange = TRUE), 
         yaxis = list(title = "Count", fixedrange = TRUE)) %>% 
  config(displayModeBar = FALSE)
```

## Buyers Backlog Trend

### All Actionable Backlog Reqs

```{r echo=FALSE, warning=FALSE, out.width="100%", out.height="500px", eval = use_time_machine}
backlog_plain_timemachine_inv_plot <- backlog_plain_timemachine %>% 
  filter(Category == "INV") %>% 
  plot_ly() %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "INV") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE))

backlog_plain_timemachine_ninv_plot <- backlog_plain_timemachine %>% 
  filter(Category == "NINV") %>% 
  plot_ly() %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "NINV") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE))

backlog_plain_timemachine_se_plot <- backlog_plain_timemachine %>% 
  filter(Category == "SE") %>% 
  plot_ly() %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "SE") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE))

subplot(backlog_plain_timemachine_inv_plot, 
        backlog_plain_timemachine_ninv_plot, 
        backlog_plain_timemachine_se_plot, 
        nrows = 3, 
        margin = .03) %>% 
  config(displayModeBar = FALSE)
```

### Req Older than 90 Days Trend

```{r echo=FALSE, warning=FALSE, out.width="100%", out.height="500px", eval = use_time_machine}
backlog_timemachine_90dayplus_sum_inv_plot <- backlog_timemachine_90dayplus_sum %>% 
  filter(Category == "INV") %>% 
  plot_ly() %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "INV") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE))

backlog_timemachine_90dayplus_sum_ninv_plot <- backlog_timemachine_90dayplus_sum %>% 
  filter(Category == "NINV") %>% 
  plot_ly() %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "NINV") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE))

backlog_timemachine_90dayplus_sum_se_plot <- backlog_timemachine_90dayplus_sum %>% 
  filter(Category == "SE") %>% 
  plot_ly() %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "SE") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE))

subplot(backlog_timemachine_90dayplus_sum_inv_plot, 
        backlog_timemachine_90dayplus_sum_ninv_plot, 
        backlog_timemachine_90dayplus_sum_se_plot, 
        nrows = 3, 
        margin = .03) %>% 
  config(displayModeBar = FALSE)
  
```
*Includes Out-to-bid and on Hold Reqs.*

Using data obtained at `r data_date`. Code version `r code_version`.

