---
output: html_document
---

```{r include=FALSE, warning=FALSE}
print("Buyer Backlog R Scipt")
library(lubridate)
source("./data_import.r")
source("./buyer-backlogs.r")
source("./buyer-backlogs-90dayplus.r")
source("./buyer-backlogs-amounts.r")
source("./approver-backlogs.r")

# Switch for whether Time Machine graphs should be displayed. Since Titles
#   for those sections are rendered independently the switch below is for
#   debug purposes only. ...and it should belong to somewhere else.
use_time_machine = TRUE

# NOTE: The following file writes to the specified mongodb, comment out
#         the line while debugging to avoid accidental writes
source("./time_machine-mongo.r")
source("./time_machine-graphs.r")
```
# Buyer Backlog Report of `r data_date`

### All Reqs

```{r echo=FALSE, warning=FALSE, fig.align='center', out.width="100%", out.height="450px"}
backlog_plot_ninv <- backlog_plot %>% 
  filter(Category == "NINV") %>% 
  plot_ly() %>% 
  add_bars(y = ~Buyer,
          x = ~Count,
          color = ~Type,
          type = "bar", 
          colors = c("#99D594","#FFFFBF","#FC8D59"),
          width = "18px",
          legendgroup = ~Type) %>% 
  layout(yaxis = list(autorange = "reversed", fixedrange = TRUE), 
         xaxis = list(fixedrange = TRUE), 
         barmode = 'stack')

backlog_plot_se <- backlog_plot %>% 
  filter(Category == "SE") %>% 
  plot_ly() %>% 
  add_bars(y = ~Buyer,
          x = ~Count,
          color = ~Type,
          type = "bar", 
          colors = c("#99D594","#FFFFBF","#FC8D59"),
          legendgroup = ~Type, 
          width = "18px",
          showlegend = F) %>% 
  layout(yaxis = list(autorange = "reversed", fixedrange = TRUE), 
         xaxis = list(fixedrange = TRUE), 
         barmode = 'stack')

backlog_plot_inv <- backlog_plot %>% 
  filter(Category == "INV") %>% 
  plot_ly() %>% 
  add_bars(y = ~Buyer,
          x = ~Count,
          color = ~Type,
          type = "bar", 
          colors = c("#99D594","#FFFFBF","#FC8D59"),
          legendgroup = ~Type, 
          width = "18px",
          showlegend = F) %>% 
  layout(yaxis = list(autorange = "reversed", fixedrange = TRUE), 
         xaxis = list(fixedrange = TRUE), 
         barmode = 'stack')

# subplots are ggplot equivalent of facets
subplot(backlog_plot_ninv, backlog_plot_se, backlog_plot_inv, nrows = 3, margin = .03, shareX = TRUE) %>% 
  config(displayModeBar = FALSE)

```
*Omitted buyer(s) with no backlogs: `r paste(hidden_buyers)`.*

### Reqs Over 90 Days 

```{r echo=FALSE, out.width="100%", out.height="375px"}

backlog_plot_90dayplus_ninv <- backlog_plot_90dayplus %>% 
  filter(Category == "NINV") %>% 
  plot_ly() %>% 
  add_bars(y = ~Buyer,
          x = ~Count,
          color = ~Type,
          type = "bar", 
          colors = c("#99D594","#FFFFBF","#FC8D59"),
          width = "18px",
          legendgroup = ~Type) %>% 
  layout(yaxis = list(autorange = "reversed", fixedrange = TRUE), 
         xaxis = list(fixedrange = TRUE), 
         barmode = 'stack')

backlog_plot_90dayplus_se <- backlog_plot_90dayplus %>% 
  filter(Category == "SE") %>% 
  plot_ly() %>% 
  add_bars(y = ~Buyer,
          x = ~Count,
          color = ~Type,
          type = "bar", 
          colors = c("#99D594","#FFFFBF","#FC8D59"),
          width = "18px",
          legendgroup = ~Type,
          showlegend = F) %>% 
  layout(yaxis = list(autorange = "reversed", fixedrange = TRUE), 
         xaxis = list(fixedrange = TRUE), 
         barmode = 'stack')

backlog_plot_90dayplus_inv <- backlog_plot_90dayplus %>% 
  filter(Category == "INV") %>% 
  plot_ly() %>% 
  add_bars(y = ~Buyer,
          x = ~Count,
          color = ~Type,
          type = "bar", 
          colors = c("#99D594","#FFFFBF","#FC8D59"),
          width = "18px",
          legendgroup = ~Type,
          showlegend = F) %>% 
  layout(yaxis = list(autorange = "reversed", fixedrange = TRUE), 
         xaxis = list(fixedrange = TRUE), 
         barmode = 'stack')


subplot(backlog_plot_90dayplus_ninv, backlog_plot_90dayplus_se, backlog_plot_90dayplus_inv, nrows = 3, margin = .03, shareX = TRUE) %>% 
  config(displayModeBar = FALSE)

```

## PP's Approval Worklist

```{r echo=FALSE}
kable(approval_kable) %>% 
  kable_styling() %>% 
  add_header_above(c("Grouping By Age (Days)" = 4, "Grouping By Dollar Amount" = 4, " " = 1)) %>% 
  column_spec(9, bold = TRUE) %>% 
  column_spec(c(4), border_right = TRUE, include_thead = TRUE)
```

<P style="page-break-before: always">

### PP's Worklist Details (`r approval_detail_count`)

*Omitted `r (approval_total_count - approval_detail_count)` entries less than $50,000.*


```{r echo=FALSE}
kable(approval_detail_table)%>% 
  kable_styling() %>% 
  add_header_above(c(" " = 1, "Worklist Data" = 3,"Req Details" = 2))
```
<P style="page-break-before: always">

## All Backlog, By Req Age
```{r echo=FALSE}
# This vector holds the buyer counts for this kable, in "NI, SE, INV" order, then add 1 for subtotal line.
# group_rows uses the vector as is for each group.
# row_spec uses cumsum of this value to get the index of last lines of each category
# The index of final Sum row is the sum of the row #s + 1. 
backlog_age_row_num_vec <- as_vector(backlog_age_kable_col_count[[2]]) + 1
kable(backlog_kable) %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 1, "Actionable" = 4, "On Hold" = 1, "Out-to-Bid" = 1, " " = 1)) %>% 
  group_rows(index = c("Non-Inventory" = backlog_age_row_num_vec[1], 
                       "Sourcing Exec." = backlog_age_row_num_vec[2], 
                       "Inventory" = backlog_age_row_num_vec[3],
                       "Total" = 1)) %>% 
  row_spec(cumsum(backlog_age_row_num_vec), italic = TRUE, background = "#EEEEEE") %>% 
  row_spec(sum(backlog_age_row_num_vec) + 1, bold = TRUE)
```
<P style="page-break-before: always">

## Backlog older than 90 days, By Req Amount

```{r echo=FALSE}
backlog_amt_row_num_vec <- as_vector(backlog_amt_kable_col_count[[2]]) + 1
kable(backlog_amount_kable) %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 1, "Actionable" = 3, "On Hold" = 1, "Out-to-Bid" = 1, " " = 1)) %>% 
  group_rows(index = c("Non-Inventory" = backlog_amt_row_num_vec[1], 
                       "Sourcing Exec." = backlog_amt_row_num_vec[2], 
                       "Inventory" = backlog_amt_row_num_vec[3], 
                       "Total" = 1)) %>% 
  row_spec(cumsum(backlog_amt_row_num_vec), italic = TRUE, background = "#EEEEEE") %>% 
  row_spec(sum(backlog_amt_row_num_vec) + 1, bold = TRUE)
```

## PP's Worklist Trend
```{r echo=FALSE, warning=FALSE, out.width="100%", out.height="400px", eval = use_time_machine}
plot_ly(data = approval_worklist_timemachine) %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "PP's List (> $50K)") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE)) %>% 
  config(displayModeBar = FALSE)

```

## Buyers Backlog Trend

### All Backlog Reqs

```{r echo=FALSE, warning=FALSE, out.width="100%", out.height="400px", eval = use_time_machine}
backlog_plain_timemachine_inv_plot <- backlog_plain_timemachine %>% 
  filter(Category == "INV") %>% 
  plot_ly() %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "INV") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE))


backlog_plain_timemachine_ninv_plot <- backlog_plain_timemachine %>% 
  filter(Category == "NINV") %>% 
  plot_ly() %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "NINV") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE))

backlog_plain_timemachine_se_plot <- backlog_plain_timemachine %>% 
  filter(Category == "SE") %>% 
  plot_ly() %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "SE") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE))

subplot(backlog_plain_timemachine_inv_plot, backlog_plain_timemachine_ninv_plot, backlog_plain_timemachine_se_plot) %>% 
  config(displayModeBar = FALSE)
```

### Req Older than 90 Days Trend

```{r echo=FALSE, warning=FALSE, out.width="100%", out.height="400px", eval = use_time_machine}
backlog_plain_timemachine_90dayplus_inv_plot <- backlog_plain_timemachine_90dayplus %>% 
  filter(Category == "INV") %>% 
  plot_ly() %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "INV") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE))

backlog_plain_timemachine_90dayplus_ninv_plot <- backlog_plain_timemachine_90dayplus %>% 
  filter(Category == "NINV") %>% 
  plot_ly() %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "NINV") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE))

backlog_plain_timemachine_90dayplus_se_plot <- backlog_plain_timemachine_90dayplus %>% 
  filter(Category == "SE") %>% 
  plot_ly() %>% 
  add_lines(x = ~Archive_Time, y = ~Cnt, name = "SE") %>% 
  layout(xaxis = list(title = "Date", fixedrange = TRUE), yaxis = list(title = "Count", fixedrange = TRUE))

subplot(backlog_plain_timemachine_90dayplus_inv_plot, backlog_plain_timemachine_90dayplus_ninv_plot, backlog_plain_timemachine_90dayplus_se_plot) %>% 
  config(displayModeBar = FALSE)
  

```
Using data obtained at `r data_date`. Code version `r code_version`.
